Standalone Tactics using OpenTheory

### 2012-01-26 paper.tex
start on 2.2

<Intro to LCF kernel? Viewing tactics as derived inference rules?>

@@

\subsection{Isolating tactics from their home systems}
Implementation details to make standalone.
<requires opentheory reader and writer for the system. so far accomplished by instrumenting the kernel to log primitive inferences. this is work, but has the additional benefit of allowing import/export of theories in opentheory repositories>
<either use Polyml.export or checkpointing to capture a function that reads a goal article, runs the tactic (recording the proof), and writes the proof article back>

Implementation details to put on the web.
<simple cgi - worth mentioning?>

>>>>

<more concrete examples? definition of tactics? viewing tactic as derived inference rule? intro to LCF kernel?>

@@

\subsection{Isolating tactics from their home systems}
There are two approaches to obtaining a standalone tactic: either write one directly, or extract an existing tactic from a proof assistant. 
We have experimented with the second approach, taking tactics from HOL4 and from HOL Light.
<The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.>
The key requirements of the proof assistant are:
\begin{enumerate}
\item
An \OpenTheory article file reader and writer,
\item
A facility for recording proofs and converting them to use the \OpenTheory primitive inferences, and,
\item
A facility for checkpointing the proof assistant, or for extracting a standalone executable encompassing the tactic functionality.
\end{enumerate}
<first two items are the most work, but have the additional benefit of allowing import/export of theories in opentheory repositories>
<in HOL4 and HOL Light, item 2 is accomplished by augmenting the internal theorem type with a type of proofs, to track primitive inferences used. this step is made easy because of the LCF architecture>
<either use Polyml.export or checkpointing to capture a function that reads a goal article, runs the tactic (recording the proof), and writes the proof article back>

<Implementation details to put on the web.>
<simple cgi - worth mentioning?>
